Computing Restricted Isometry Constants via Mixed-Integer Semidefinite Programming

### 2016-03-23 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
corrected adress

\title{Computing Restricted Isometry Constants via Mixed-Integer Semidefinite Programming}
\author{Tristan~Gally and Marc~E.~Pfetsch
  \thanks{This work was supported by the German Research Foundation (DFG) through Collaborative Research Center 805 and Priority Program 1798.}
  \thanks{The  authors  are  with  the  Research  Group  Optimization,  TU
    Darmstadt, Dolivostr.\ 5,
  Darmstadt  64293,  Germany  (e-mail:  gally@opt.tu-darmstadt.de;
  pfetsch@opt.tu-darmstadt.de).}}

>>>>

\title{Computing Restricted Isometry Constants via Mixed-Integer Semidefinite Programming}
\author{Tristan~Gally and Marc~E.~Pfetsch
  \thanks{This work was supported by the German Research Foundation (DFG) through Collaborative Research Center 805 and Priority Program 1798.}
  \thanks{The  authors  are  with  the  Research  Group  Optimization,  TU
    Darmstadt, Dolivostr.\ 15,
  Darmstadt  64293,  Germany  (e-mail:  gally@opt.tu-darmstadt.de;
  pfetsch@opt.tu-darmstadt.de).}}
